---
title: "LaTeX"
output: html_document
---

```{r setup, include=FALSE}
xaringanExtra::use_panelset()
knitr::opts_chunk$set(echo = FALSE)
```

```{r, child="custom-buttons.Rmd"}
```

<!--#region items -->

<div class='level3'>
- **Cheat sheet** \
This 
[summary](https://courses.edx.org/assets/courseware/v1/29eb39fb3d98de8923beb13401ac62ba/asset-v1:IITBombayX+LaTeX101x+1T2021+type@asset+block/CheatSheet_LaTeX_2019_11_13_Firuza.pdf)
of LateX commands is from an online LateX course.
<p style="margin-bottom: -10px;">&nbsp;</p>
</div>

<div class='level2'>
- **List of LateX symbols** \
[The Comprehensive LATEX Symbol List](http://tug.ctan.org/info/symbols/comprehensive/symbols-a4.pdf)
<p style="margin-bottom: -10px;">&nbsp;</p>
</div>

<div class='level1'>
- **LateX fonts** \
[The LateX Font Catalogue](https://www.tug.org/FontCatalogue/)
<p style="margin-bottom: -10px;">&nbsp;</p>
</div>

<div class='level2'>
- **Customize geometry of Rmarkdown pdf output** \
You can set the geometry in the YAML section. \
Examples:
```yaml
geometry: "left=5em,top=2.5em,right=5em,bottom=6em"

geometry: "landscape"
```
<p style="margin-bottom: -10px;">&nbsp;</p>
</div>

<div class='level1'>
- **Math equations** \
```md
\( ... \) for inline math expressions.
\[ ... \] for display-style expressions.
```
<p style="margin-bottom: -10px;">&nbsp;</p>
</div>

<div class='level2'>
- **Include LateX packages in rmd file** \
In the YAML section of the Rmarkdown document include some text as in the following example: \
```yaml
header-includes:
    - usepackage{unicode-math}
    - usepackage{ragged2e}
```
<p style="margin-bottom: -10px;">&nbsp;</p>
</div>

<div class='level2'>
- **Pdf output** \
In order to avoid certain problems with LateX when the ouput file is pdf, 
I suggest you add the following to the YAML section of the rmd document:
```yaml
output: 
pdf_document:
    latex_engine: xelatex
```
<p style="margin-bottom: -10px;">&nbsp;</p>
</div>

<div class='level3'>
- **Efficient way to find the LateX code for symbols** \
This [site](http://detexify.kirelabs.org/classify.html) allows you to draw
a symbol and it will output various possibilities for which LateX code to
use in order to use that symbol (or an approximation of it in case your
drawing is kinda bad).
<p style="margin-bottom: -10px;">&nbsp;</p>
</div>

<div class='level1'>
- **Spacing** \
The ragged2e package does not seem to work when the output is html, 
but it does when the output is a pdf file. In that case, you may use
functions such as
```latex
\kern2em
\vspace{1ex}
\hspace{10ex}
```
<p style="margin-bottom: -10px;">&nbsp;</p>
</div>

<div class='level1'>
- **Inline display style** \
For prettier inline math equations can be made possible for symbols like
`\int, \lim, \prod, ...`,  via `\displaystyle{ }`. \
Comparison: \
`\lim_{h\to\, 0}` \( \quad\Rightarrow\quad \lim_{h\to\, 0} \quad .\) \
`\displaytyle{\lim_{h\to\, 0}}` \( \quad\Rightarrow\quad \displaystyle{\lim_{h\to\, 0}} \quad.\)  
<p style="margin-bottom: -10px;">&nbsp;</p>
</div>

<div class='level1'>
- **Cartesian product symbol** \
\( \times \) as ` \times `
<p style="margin-bottom: -10px;">&nbsp;</p>
</div>

<div class='level1'>
- **Function composition symbol** \
\( \circ \) as ` \circ `
<p style="margin-bottom: -10px;">&nbsp;</p>
</div>

<div class='level1'>
- **Reverse symbol of _belongs in_** \
\( \in \) as `\in` and \( \ni \) as `\ni`.
<p style="margin-bottom: -10px;">&nbsp;</p>
</div>

<div class='level1'>
- **Inner product symbol** \
`\langle u,v \rangle` \( \quad\Rightarrow\quad \langle u,v \rangle \, .\)
<p style="margin-bottom: -10px;">&nbsp;</p>
</div>

<div class='level2'>
- **Basic structure of a book in LateX** \
```latex
documentclass{book}
\title{LaTeX Document}
\author{Wikipedia \\ Collated by Firuza}
\date{\today}
\begin{document}
\maketitle
\tableofcontents

\chapter{Overview}

\section{Overall Description}

\section{Introduction}
\paragraph{}
Dhansak is a popular Indian dish, originating among the Parsi Zoroastrian community.

\subsection{Purpose}
\end{document}
```
<p style="margin-bottom: -10px;">&nbsp;</p>
</div>

<div class='level1'>
- **Avoid entry in table of contents** \
Possible using \* as in the following examples:
```latex
\chapter*{Introduction}
\subsection*{Time-table}
```
<p style="margin-bottom: -10px;">&nbsp;</p>
</div>

<div class='level1'>
- **Proper quotes use** \
\` for the opening of quotes, and \' for closing them.
<p style="margin-bottom: -10px;">&nbsp;</p>
</div>

<div class='level2'>
- **Set margin of the pages** \
Example:
```latex
% Write between documentclass{article} and begin{document}
\usepackage[a4paper,margin=2in]{geometry} % 2 inches in all 4 sides of the page
\usepackage[a5paper,top=1in,left=2in,right=0.75in,bottom=1in]{geometry}

% Write between documentclass{book} and begin{document}
\usepackage[inner= 1.5in,outer=0.5in]{geometry}
```
<p style="margin-bottom: -10px;">&nbsp;</p>
</div>

<div class='level1'>
- **Remove page numbering** \
```latex
% Insert in the document environment
\pagenumbering{gobble}
```
<p style="margin-bottom: -10px;">&nbsp;</p>
</div>

<div class='level2'>
- **Customize the page numbering** \
For a book document class, one can set when to start counting the pages via 
`\setcounter{page}{1}`. \
I prefer the following customization for the beggining of a book:
```latex
\begin{document}
\maketitle
\pagenumbering{gobble}

\tableofcontents
\pagenumbering{roman}

\chapter{Introduction}
\setcounter{page}{1}
\pagenumbering{arabic}

\section{blank}
% ...

\end{document}
```
<p style="margin-bottom: -10px;">&nbsp;</p>
</div>

<div class='level1'>
- **Rotate page content by 90 degrees** \
```latex
\usepackage{lscape}

\begin{document}

\begin{landscape}
    
    Content to be presented in the rotated page.

\end{landscape}

\end{document}
```
<p style="margin-bottom: -10px;">&nbsp;</p>
</div>

<div class='level1'>
- **Make pdf easier to read online** \
If the pdf document will most likely be read in a pc,
it becomes easier to do so if you include 
`\usepackage[landscape]{geometry}`. That way, everything
inside the document environment will be affected by the 
landscape environment.
<p style="margin-bottom: -10px;">&nbsp;</p>
</div>

<div class='level2'>
- **Page break vs new page** \
From stackexchange: \
`\pagebreak` tries to make the page the same height as other pages if it's possible (by stretching intervals between paragraphs etc) 
and `\newpage` just fills the page with empty space.
<p style="margin-bottom: -10px;">&nbsp;</p>
</div>

<div class='level1'>
- **Insert footnote** \
Example:
```latex
% Inside the document environment
    arbitrary text to be footnoted \footnote{content of this footnote}
```
<p style="margin-bottom: -10px;">&nbsp;</p>
</div>

<div class='level2'>
- **Column formatting** \
* For just two columns, you can set 
`\documentclass[twocolumn]{...}`.

* For more than two columns, no need to alter the documnt class,
but add instead `\usepackage{multicol}` and incude the text to be 
_columnized_ in the proper environment:
```latex
\begin{multicols}{n} % n is the number of columns
% content
\end{multicols}
```

* Change the distance between columns with
`	\setlength{\columnsep}{20pt}`, where its last argument defines such distance.

* Add a bar to separate the columns with 
`	\setlength{\columnseprule}{1pt}`, where its last argument defines the thickness of the bar.

* Set where to start the next column with 
`\columnbreak` .
<p style="margin-bottom: -10px;">&nbsp;</p>
</div>

<div class='level1'>
- **Changing font size** \
To set the new font size for the rest of the document, type, for example, 
`\large`; but, if you only want to apply a font size to a specific part of the text,
type, for example, `{\large content ...}` .
<p style="margin-bottom: -10px;">&nbsp;</p>
</div>

<div class='level1'>
- **Customizing text color** \
Example: 
```latex
\documentclass{article}
\usepackage[dvipsnames]{xcolor} 

\begin{document}

% Mix white with 60% of red
\pagecolor{red!60}    

% Mix blue with 10% of red
\textcolor{red!10!blue}{texto}

\end{document}
```
<p style="margin-bottom: -10px;">&nbsp;</p>
</div>

<div class='level1'>
- **Aligning text** \
By default, LateX's text is fully justified, but you can change it via:
```latex
\begin{document}

\centering
texto

\flushleft
texto

\flushright
texto

\justify    % This one requires the package ragged2e
texto

\end{document}
```
<p style="margin-bottom: -10px;">&nbsp;</p>
</div>

<div class='level1'>
- **Spacing** \
```latex
% For the space between lines of text, the following commands set a new standard for the WHOLE document:
\singlespacing
\onehalfspacing
\doublespacing

% You can also set a custom spacing using the setspace package:
\spacing{X}

\begin{spacing}{X}
...
\end{spacing}

% Basic vertical spacing commands:
\vspace{Xpt}
\smallskip
\medskip
\bigskip
\vfill    % Very useful for typing the "cover" of a document.

% Basic horizontal spacing commands:
\    % Adds a single space
\,
\hspace{Xpt}
\hfill
```
<p style="margin-bottom: -10px;">&nbsp;</p>
</div>

<div class='level1'>
- **Create lists** \
```latex
% Types of lists
\begin{itemize | enumerate | description}
\item ...
\item [...] ...    % Used only with description
\end{itemize | enumerate | description}

% There is a limitation of 4 levels (list inside list) nesting.

% Change numbering style
\usepackage{enumerate} \begin{enumerate}[...]

% Change bullet Style
\usepackage{amssymb}
\renewcommand{\labelitem<Level>}{$<Style>$}

Examples:
\renewcommand{\labelitemi}{$ \diamond $}
\renewcommand{\labelitemii}{$ \cdot $}
```
<p style="margin-bottom: -10px;">&nbsp;</p>
</div>

<div class='level2'>
- **Create matrix** \
Example:
```latex
% Requires the package amsmath 
$
\begin{pmatrix}			  % ( ) symbols for matrix
    a_{11} & a_{12} \\    % New row 
    a_{21} & a_{22} 		
\end{pmatrix}
\kern2em
\begin{bmatrix}			  % [ ] symbols for matrix
    a_{11} & a_{12} \\     
    a_{21} & a_{22} 		
\end{bmatrix}
$

% No extra package required

\[ \left(\begin{array}{ccc}
1 & 2 \\
2 & 4 
\end{array}\right) \]
```
<p style="margin-bottom: -10px;">&nbsp;</p>
</div>

<div class='level2'>
- **Create equation** \
Example:
```latex
\begin{equation}
    \cos^2 x - \sin^2 x = \cos(2x)
\end{equation}
% It automatically becomes centered and the equation number is displayed.
```
<p style="margin-bottom: -10px;">&nbsp;</p>
</div>

<div class='level2'>
- **Align equations** \
Example:
```latex
% Requires the package amsmath 
\begin{align}
    x^2 - 2x &= -1   \\			      % New line 
    x^2 -2x +1 &= 0  \nonumber\\  
    % The & symbol sets the following character in the same horizontal position
    (x-1)^2 &= 0     \nonumber\\
    x &= 1 			     \nonumber   
    % \nonumbber means "do not label this equation"
\end{align}
```
<p style="margin-bottom: -10px;">&nbsp;</p>
</div>

<div class='level2'>
- **Create a table** \
Example:
```latex
\begin{tabular}{clrp{4cm}}
No. & Item & Price & Qty \\ 
1   & Mouse & 10 &  1    \\
% & separates columns
% \\ is for new row
% c: center; l: left; r: right
% p{Xcm} sets a length of X cm for such column.
\end{tabular}
```
Add lines:
```latex
\begin{tabular}{|c|l|l|r|}    % Each | is a vertical line
\hline    % horizontal line
No. & Item & Quantity & Price \\
\hline
1 & Pen & 3 & 10 \\
\cline{1-2} \cline{4-4}    
% Horizontal line between columns 1 and 2
% Horizontal line for column 4
2 & Pencil & & 5 \\
\hline
\end{tabular}
```
You can use the package `arydshln` to apply dashed lines instead, via:
```latex
\hdashline[size of dash / space between dashes]
\cdashline {i-j}[size of dash / space between dashes]
% The vertical dashed line is used with, for example:
% \begin{tabular}{:c:l:l:r:}
```
<p style="margin-bottom: -10px;">&nbsp;</p>
</div>

<div class='level2'>
- **Merge table's rows or columns** \
Merge rows:
```latex
% Requires the package multirow and the command
% \multirow{Numbe_of_rows}{width}{content}
% Example:
\begin{tabular}{|c|l|l|r|}
\hline
No. & Item & Quantity & Price \\
\hline
1 & Pen & \multirow{2}{*}{3} & 10 \\
...
% The * symbol is to keep the previously length of such column
% Rows 2 and 3 got merged
```
Merge columns:
```latex
% Does not require to add a package
% Example:
\begin{tabular}{|c|l|l|r|}
\hline
\multicolumn{4}{|c|}{Stationery Items} \\ 
% Four columns have been merged
\hline
No. & Item & Quantity & Price \\
...
```
<p style="margin-bottom: -10px;">&nbsp;</p>
</div>

<div class='level2'>
- **Change the spacing for tables** \
Insert the command 
`\renewcommand{\arraystretch}{value}`
before the tabular environment. The default "value" is 1,
but 1.5 works better, in my opinion.
<p style="margin-bottom: -10px;">&nbsp;</p>
</div>

<div class='level2'>
- **Table that spans more than one page** \
To address this problem, when using the tabular environment,
use the package `longtable` and change the environment of the 
table to `longtable`, instead of tabular. \
If you wish that the first \( n \) rows of your table get repeated
in every page that your table spans, insert `\endhead` right after
the last row you wish to be repeated.
<p style="margin-bottom: -10px;">&nbsp;</p>
</div>

<div class='level2'>
- **Table environment** \
It allows us to add captions and change the position of the table: \
* Environment:
```latex
\begin{table}[position]
    your tabular code
    \caption{...}
\end{table}

% Position:
% t: Insert table at top of the page.
% b: Insert table at bottom of the page.
% h: Insert table approximately here.
```

* You can create a "table of contents" analogue for the tables, 
via the command `\listoftables` .
<p style="margin-bottom: -10px;">&nbsp;</p>
</div>

<div class='level2'>
- **Include images** \
It requires the `graphicx` package, which supports  
jpg, png, eps and pdf files. The image must be in the same folder as the tex file.

* Scaling
```latex
\includegraphics{image.jpg}
\includegraphics[height=4cm]{image.pdf}
\includegraphics[width=4cm]{image.png}

% The following example is not recommended, due to changing the 
% proportions of the image.
\includegraphics[width=4cm, height=4cm]{image.eps}

\includegraphics[scale=0.5]{image.png}
```

* Crop
```latex
\includegraphics[clip=true, trim=15mm 5mm 7mm 3mm]{image.png}
```

* Rotate 
```latex
\includegraphics[angle=60]{image.png}
```

* Add an image border
```latex
\fbox{ \includegraphics... }

% Adjust the border thickness with:
\setlength{\fboxrule}{2pt}

% Change the distance bewtween the image 
% and its border with:
\setlength{\fboxsep}{15pt}

% Both last commands only affect the
% \includegraphics{...} that appear after them.
```
<p style="margin-bottom: -10px;">&nbsp;</p>
</div>

<div class='level2'>
- **The figure environment** \
It allows us to position the figure and add a caption to it. \
Example:
```latex
\begin{figure}[position]
\includegraphics[...]{...}
\caption{...}
\end{figure}
```
You can add a "table of contents" analogue for the figures with
`\listoffigures`  .

* Add sub-figures
It requires the packages `caption` and `subcaption`  .\
Basic structure:
```latex
\begin{figure}[<position>]
    \begin{subfigure}{<width>}
    \includegraphics...
    \caption{...}
    \end{subfigure}
    ...
    \caption{...}
\end{figure}
```
Example: 
```latex
\begin{figure}
    \centering
    \begin{subfigure}{0.3\textwidth}
    % Notice the necessary "0.3" because we include 3 figures.
    % For just two figures, "0.4" would have sufficed.
    \centering
    \includegraphics[width=\textwidth]{image.png}
    \caption{Original Image}
    \end{subfigure}
    \hfill % So that the sub figures aren't right next to each other.
    \begin{subfigure}{0.3\textwidth}
    \centering
    \includegraphics[width=\textwidth, angle=90]{images/parrot.png}
    \caption{Rotated by 90 degrees}
    \end{subfigure}	
    \hfill
    \begin{subfigure}{0.3\textwidth}
    \centering
    \includegraphics[width=\textwidth, angle=90]{images/parrot.png}
    \caption{Rotated by 90 degrees}
    \end{subfigure}	
    \caption{Image of a Parrot}
\end{figure}
```
If you leave blank lines in the figure environment, the subfigures may not be shown in the same line. \
To remove the \"(a)\" automatic label of the subfigure caption, include 
`\captionsetup[subfigure]{labelformat=empty}` in the beggining of the document environment.
<p style="margin-bottom: -10px;">&nbsp;</p>
</div>

<div class='level1'>
- **Creating the cover** \
It's done in the `titlepage` environment. \
Example:
```latex
\begin{titlepage}
    \centering
    
    \huge
    \textbf{Car\'atula}
    \vfill
    
    \Large
    \textbf{Submited by } \\
    \medskip
    Lucio Cornejo
    \vfill
    
    PUCP
    \vfill
    
    August  4
    \vfill
    
    2021	
\end{titlepage}
```
LateX will automatically not number the page of \"titlepage\",
and it will begin counting the pages from the next page instead.
<p style="margin-bottom: -10px;">&nbsp;</p>
</div>

<div class='level1'>
- **Include hyperlinks and hypertext** \
It requires the packages `url` and `hyperref`. \
Display a link with, for example,
`\url{https://www.google.com/}`  . \
Create hypertext with 
`\href{https://www.overleaf.com}{Overleaf}`, 
where the second \{ \} contains what will be displayed but 
takes you when clicked to the url denoted.
<p style="margin-bottom: -10px;">&nbsp;</p>
</div>

<div class='level2'>
- **Cross referencing** \
Label a section, subsection, table, figure or page number via `\label{KEY}`,
and refer to them via the following:
```latex
\ref{KEY}     % Outputs the index number of such object labelled.
\pageref{KEY} % Outputs the page number of such object labelled.

% This command requires the package hyperref
\nameref{KEY} % Outputs the bane of such object labelled.
```
<p style="margin-bottom: -10px;">&nbsp;</p>
</div>

<div class='level3'>
- **Beamer presentation** \
    * Creation \
    Set `beamer` as the document class.

    * Themes \
    [Here](https://hartwork.org/beamer-theme-matrix/)
    are some popular themes and colorthemes for beamer. \
    Example:
    ```latex
    \usetheme{Berkeley}
    \usecolortheme{default}
    ```

    * Create a slide \
    ```latex
    \begin{frame}[t|c|b]{Frame Title}
    ...
    \end{frame}

    % The [.] and {.} next to {frame} are optional.
    % [t] sets the content to the top of the page;
    % [b], to the bottom, and; [c], to the center.
    ```

    * Table of contents \
    Same command: `\tableofcontents`

    * Insert boxes \
    ```latex
    % Add block
    \begin{block}{Title}
    ...
    \end{block}

    % Add alert 
    \begin{alertblock}{Title}
    ...
    \end{alertblock}

    % Add example(s)
    \begin{example}
    ...
    \end{example} 
    % The example environment does not allow to set it a title.
    ```

    * Insert columns \
    ```latex
    % Environment
    \begin{columns}
    \column{X\textwidth}
    content of this particular column
    ...
    \end{columns}
    ```

    * Automatically add necessary frames \
    If one frame environment contains so much content that not all of it can get displayed in 
    one slide, simply change the frame environment as follows: \
    ```latex
    \begin{frame}[allowframebreaks]{title}    
    ...
    \end{frame}
    ```
    Now the missing content will be displayed in the necessary amount of slides.

    * Set a pause \
    You can pause the display of lists, blocks, text, etc. \
    Example:
    ```latex
    \begin{frame}
    \begin{itemize}
        \item 1 \pause
        \item 2 \pause
    \end{itemize}

    \vfill

    \begin{itemize}
        \item<2-> 1  % Show this item second.
        \item<1-> 2  % Show this item first.
    \end{itemize}
    \end{frame}

    \begin{frame}
    \begin{block}{Theorem}
        \pause
        For all $ \theta \in \mathbb{R} $, it holds 
        $ \cos^2\theta + \sin^2\theta = 1 \; . $
    \end{block}
    \pause

    \begin{alertblock}{Extra}
        Also true if $ \theta $ is a complex number.
    \end{alertblock}
    \end{frame}
    ```

    * Change view of about to be displayed content \
    ```latex
    % Show in transparent the content about to be displayed
    \setbeamercovered{transparent}

    % Hide the content about to be displayed
    \setbeamercovered{invisible}
    ```

    * Special title, author, institution and logo \
    Sometimes the set `\title{...}, \author{...}, ...`  can be too long to fit in
    the space provided by the beamer theme used. Therefore, you can add alternative 
    values to those categories to appear in the proper beamer section. \
    Example:
    ```latex
    \documentclass{beamer}
    \usetheme{Madrid}
    \usecolortheme{default}

    \title[Animals and Flowers]{Basic Information about Wild Animals and Flowers}
    \author[Firuza]{Firuza Karmali}
    \institute[IIT Bombay]{{\large Indian Institute of Technology Bombay}}
    \logo{\includegraphics[height=1cm]{pi.jpg}}

    % The content in [] will appear in the bottom section of each beamer slides,
    % while the content in {} will appear in the slide where \maketitle is applied.
    % The logo will appear at the bottom right of every slide.
    ```

    * Change the color of objects in Beamer\
    ```latex
    % Theme color
    \setbeamercolor{structure}{fg=color}

    % Tertiary
    \setbeamercolor{palette tertiary}{bg=color, fg=color}

    % Secondary
    \setbeamercolor{palette secondary}{bg=color, fg=color}

    % Primary
    \setbeamercolor{palette primary}{bg=color, fg=color}

    % Title
    \setbeamercolor{title}{bg=color, fg=color}

    % Frame Title
    \setbeamercolor{frametitle}{bg=color, fg=color}

    % Slide background 
    \setbeamercolor{background canvas}{bg=color}

    % You can also use the "!proportion" command to mix colors 
    % in the "color" section after "bg=" or "fg=".
    ```

    * Specify the aspect ratio of the slides
    ```latex
    % 16:9
    \documentclass[aspectratio=169]{beamer}
    % 4:3
    \documentclass[aspectratio=43]{beamer}
    ```
<p style="margin-bottom: -10px;">&nbsp;</p>
</div>

<div class='level1'>
- **Add curved line on top of symbol** \
Example: \
\( \widetilde{M} \) as `\widetilde{M}` .
<p style="margin-bottom: -10px;">&nbsp;</p>
</div>

<div class='level2'>
- **Create a diagram** \
Example: 
```latex
\documentclass{article}
\usepackage{tikz-cd}
\begin{document}
\[
\begin{tikzcd}
    U \arrow[r,"f"] &
    V  
    \\
    \widetilde{U} \arrow[u,"\varphi"]\arrow[r,swap,"Id"] &		
    \widetilde{U} \arrow[u,swap,"\phi\circ\widetilde{f}"] 
\end{tikzcd}
\]
\end{document}
```
It does not seem to work natively in Rmarkdown.
<p style="margin-bottom: -10px;">&nbsp;</p>
</div>

<div class='level1'>
- **Symbol for orthogonal vector** \
`\perp` \( \Rightarrow \; \perp\) \
`\not\perp` \( \Rightarrow \;\not\perp \)
<p style="margin-bottom: -10px;">&nbsp;</p>
</div>

<div class='level2'>
- **Horizontal braces** \
Examples: \
\( \underbrace{f \circ \alpha}_{\beta} \) as `\underbrace{f \circ \alpha}_{\beta}`. 

\( \overbrace{\mathbb{R}^n \times\cdots\times\mathbb{R}^n}^{n \text{ veces}}\) as `\overbrace{\mathbb{R}^n \times\cdots\times\mathbb{R}^n}^{n \text{ veces}}`.
<p style="margin-bottom: -10px;">&nbsp;</p>
</div>

<div class='level1'>
- **Norm symbol** \
Instead of using twice double `\mid`, try `\lVert x \rVert` for \( \lVert x \rVert \, .\)
<p style="margin-bottom: -10px;">&nbsp;</p>
</div>

<div class='level2'>
- **Insert an arrow with text on top and/or bottom** \
Example:
```latex
A\xleftarrow{n+\mu-1}B\xrightarrow[T]{n\pm i-1}C.
```
Source: <https://web.archive.org/web/20180705220556/http://www.stack.nl:80/~jwk/latex/examples/node6.html>
<p style="margin-bottom: -10px;">&nbsp;</p>
</div>


<!--#endregion-->

