---
output: html_document
---

```{r setup, include=FALSE}
xaringanExtra::use_panelset()
knitr::opts_chunk$set(echo = FALSE)
```

<div class="level-buttons" style="display: inline-flex;">
<button type="button" onclick="toggle_visibility(1)">Level 1</button>
<button type="button" onclick="toggle_visibility(2)">Level 2</button>
<button type="button" onclick="toggle_visibility(3)">Level 3</button>
<button type="button" onclick="toggle_visibility(4)">Level 4</button>
<button type="button" onclick="toggle_visibility(5)">Level 5</button>
</div>

## {.panelset}

### General

```{r}
x <- 2
x+2
```
### R Markdown

```{r}
plot(pressure)
```

### Bookdown

lorem ipsum

### Blogdown

lorem ipsum

### Shiny

lorem ipsum

### Xaringan

lorem ipsum

### Data Visualization

lorem ipsum

### CSS

<div class='level1'>
- **Limitation** \
Currently in R Markdown, CSS chunks only work with HTML output types, not with pdf. 
Although, CSS does work with the **R** package **pagedown**. \
Either way, LateX can come in handy to fix that gap.
<p style="margin-bottom: -10px;">&nbsp;</p>
</div>

<div class='level2'>
- **Useful summary from Harvard University** \
[https://cs50.harvard.edu/web/2020/notes/0/](https://cs50.harvard.edu/web/2020/notes/0/)
<p style="margin-bottom: -10px;">&nbsp;</p>
</div>

<div class='level1'>
- **Get info of object to customize it with CSS** \
Useful when the R Markdown output is html_document and you wish to customize some object from the web page.
For Google Chrome, open the html file there and right click the object which you wish to customize, then click 
"Inspeccionar"/"Inspect". A menu will appear and contain the necessary HTML data to get the **class** of the object you
wish to customize, so, use that info in a CSS chunk in the R Markdown file.
<p style="margin-bottom: -10px;">&nbsp;</p>
</div>

<div class='level1'>
- **Include a comment** \
Example of CSS chunk: \
```css
h1 {color: #EF99E3; }
/* this is a comment */
```
<p style="margin-bottom: -10px;">&nbsp;</p>
</div>

<div class='level2'>
- **Inline styling of a heading** \
Examples:
```text
<h1 style="color: blue; text-align: center;">Welcome to my page</h1>

## Section 2 {style="color:red;"}

### Section 3 {onclick="alert('wow')"}
```
<p style="margin-bottom: -10px;">&nbsp;</p>
</div>

<div class='level2'>
- **Not inline styling** \
In the `head` section of a HTML document, you can include 
the style of HTML components via `<style>`. \
Example:
```html
<head>
<title> Hello! </title>
<style>
    h1 {
    color: blue;
    text-align: center;
    }
</style>
</head>
```
`Even better version:`
```html
<head>
    <title> Hello! </title>
    <link rel="stylesheet" href="style.css">
</head>
```
Where the arbitrary file `style.css` only contains the relevant CSS code.
<p style="margin-bottom: -10px;">&nbsp;</p>
</div>

<div class='level1'>
- **Set fonts** \
Font types: <https://www.w3.org/Style/Examples/007/fonts.en.html> \
Example:
```css
div { 
font-family: Arial, sans-serif;
font-size: 28px;
font-weight: bold;
}
```
That way, the font sans-serif will be applied in case that the browser
used does not recognize the other font, Arial in this case.
<p style="margin-bottom: -10px;">&nbsp;</p>
</div>

<div class='level1'>
- **Apply styling to multiple objects** \
Example:
```html
<style>
    td,th {
        border: 1px solid black;
    padding: 5px;
}
</style>
```
<p style="margin-bottom: -10px;">&nbsp;</p>
</div>

<div class='level2'>
- **Basic table styling** \
Example:
```html
<head>
<title> Hello! </title>
<style>
    table {
        border: 1px solid black;
        border-collapse: collapse;
        text-align: center;
    }
    td,th {
        border: 1px solid black;
        padding: 5px;
    }
</style>
</head>
<body>
<table>
    <thead>
        <tr>
            <th>Nombre</th>
            <th>Sexo</th>
        </tr>
    </thead>
    <tbody>
        <tr>
            <td>Lucio</td>
            <td>M</td>
        </tr>
        <tr>
            <td>Lucía</td>
            <td>F</td>
        </tr>
    </tbody>
</table>
</body>
```
<p style="margin-bottom: -10px;">&nbsp;</p>
</div>


<div class='level2'>
- **Spacing between cells in a table** \
Example: \
```css
table {
border-spacing: 10px 15px;
}
```
Such example establishes a vertical distance of 10px and a horizontal
distance of 15px between the cells in a HTML table.
<p style="margin-bottom: -10px;">&nbsp;</p>
</div>

<div class='level1'>
- **Referencing HTML objects** \
You can use `class` to refer to a particular 
set of HTML objects; and, `id`, to refer to an unique HTML object. \
Example:
```html
<h1 id ="foo">Hello</h1>     Refer in CSS with #foo.
<h2 class="fue">Hola</h2>    Refer in CSS with .fue
```
The `specificity` CSS hierarchy  works as follows: \

1. inline 

2. id 

3. class

4. type
<p style="margin-bottom: -10px;">&nbsp;</p>
</div>

<div class='level1'>
- **Style based on attributes** \
Example:
```html
<head>
<title> Hello! </title>
<style>
    a {
        color: blue;
    }
    a[href="https://google.com"] {
        color: red;
    }
</style>
</head>
<body>
<ul>
    <li><a href="https://google.com">Google</a></li>
    <li><a href="https://facebook.com">Facebook</a></li>
</ul>
</body>
```
<p style="margin-bottom: -10px;">&nbsp;</p>
</div>

<div class='level2'>
- **Hover use of selector** \
Example:
```html
<head>
<title> Hello! </title>
<style>
    button {
        background-color: green;
    }
    button:hover {
        background-color: orange;
    }
</style>
</head>
<body>
<button>Click me</button>
</body>
```
<p style="margin-bottom: -10px;">&nbsp;</p>
</div>

<div class='level2'>
- **Media queries** \
Example:
```html
<head>
<title> Hello! </title>
<style>
    @media (min-width: 600px) {
        /*
        If width of page is 600px or larger, then perform:
        */
        body {
            background-color: red;
        }
    }
    @media (max-width: 599px) {
        /*
        If width of page is 599px or smaller, then perform:
        */
        body {
            background-color: blue;
        }
    }
</style>
</head>
<body>
    <h1>Hello, world!</h1>
</body>
```
<p style="margin-bottom: -10px;">&nbsp;</p>
</div>

<div class='level2'>
- **Automatic wrapping of HTML content as page width changes** \
Example:
```html
<head>
<title> Hello! </title>
<style>
    #test {
        display: flex;
        flex-wrap: wrap;
    }
    #test > div {
        background-color: blue;
        width: 200px;
        font-size:20px;
        margin: 20px;
        padding: 20px;
    }   
</style>
</head>
<body>
    <div id="test">
        <div>1. test </div>
        <div>2. test </div>
        <div>3. test </div>
        <div>4. test </div>
        <div>5. test </div>
        <div>6. test </div>
        <div>7. test </div>
        <div>8. test </div>
        <div>9. test </div>
        <div>10. test </div>
    </div>
</body>
```
It does not seem to work in R Markdown when the content of `<div>` is a LaTeX equation.
<p style="margin-bottom: -10px;">&nbsp;</p>
</div>

<div class='level2'>
- **Improve appearance on mobile** \
Add the following line in the head of the HTML files: \
`<meta name="viewport" content="width=device-width, initial-scale=1.0">`
<p style="margin-bottom: -10px;">&nbsp;</p>
</div>

<div class='level2'>
- **Grid** \
Example:
```html
<head>
<title>My Web Page!</title>
<meta name="viewport" content="width=device-width, initial-scale=1.0">
<style>
    .grid {
        background-color: green;
        display: grid;
        padding: 20px;
        grid-column-gap: 20px;
        grid-row-gap: 10px;
        grid-template-columns: 200px 200px auto;
    }

    .grid-item {
        background-color: white;
        font-size: 20px;
        padding: 20px;
        text-align: center;
    }
</style>
</head>
<body>
    <div class="grid">
        <div class="grid-item">1</div>
        <div class="grid-item">2</div>
        <div class="grid-item">3</div>
        <div class="grid-item">4</div>
        <div class="grid-item">5</div>
        <div class="grid-item">6</div>
        <div class="grid-item">7</div>
        <div class="grid-item">8</div>
        <div class="grid-item">9</div>
        <div class="grid-item">10</div>
        <div class="grid-item">11</div>
        <div class="grid-item">12</div>
    </div>
</body>
```
<p style="margin-bottom: -10px;">&nbsp;</p>
</div>

<div class='level2'>
- **Bootstrap** \
It's a CSS library with a lot of presets to work with. \
To work with it, add the following line in the head of the HTML files: \
`<link href="https://cdn.jsdelivr.net/npm/bootstrap@5.1.0/dist/css/bootstrap.min.css" rel="stylesheet" integrity="sha384-KyZXEAg3QhqLMpG8r+8fhAXLRk2vvoC2f3B09zVXn8CA5QIVfZOJ3BCsw2P0p/We" crossorigin="anonymous">` \
For more Information, visit this [link](https://getbootstrap.com/docs/5.1/getting-started/introduction/).\
<p style="margin-bottom: -10px;">&nbsp;</p>
</div>

<div class='level2'>
- **Bootstrap HTML templates** \
Visit this [link](https://community.rstudio.com/t/in-rstudio-R Markdown-how-to-add-new-html-themes-from-bootswatch/15791/2
https://bootswatch.com/) to download some Bootstrap HTML page stylings.
<p style="margin-bottom: -10px;">&nbsp;</p>
</div>

<div class='level3'>
- **Sass** \
It's pretty much CSS on steroids. Some of its additional features compared to CSS are `defining variables`,
`nesting` and `inheritance`. \
Its files are of the type `.scss` and web browsers do not understand it. Therefore, you need to install
`Sass` in order to convert the scss file into a css one and include it in the HTML document.
<p style="margin-bottom: -10px;">&nbsp;</p>
</div>

<div class='level2'>
- **Overwrite inline styling** \
To beat the inline `style` specification, use `!important`.\
Example:
```css
h1 {
    color: red !important;
}
```
However, CSS code already with `!important` included can not be overwritten by `!important`.
<p style="margin-bottom: -10px;">&nbsp;</p>
</div>

<div class='level1'>
- **Text sensitive attribute selectors** \
```css
/* Select every cell (with data attribute content) containing word "male" */
td[data-content="male"] {
color: red;
}

/* Select every cell starting on "p" case insensitive */
td[data-content^="p" i] {
color: blue;
}

/* Select every cell containing "4" */
td[data-content*="4"] {
color: green;
}
```
<p style="margin-bottom: -10px;">&nbsp;</p>
</div>

<div class='level1'>
- **Underline text** \
Example:
```css
div {
    text-decoration: underline;
}
```
<p style="margin-bottom: -10px;">&nbsp;</p>
</div>

<div class='level2'>
- **Underline text without breaking the line** \
Example:
```html
<p>
    Only highlight 
    <span style="text-decoration: underline;">this</span>
    word.
</p>
```
<p style="margin-bottom: -10px;">&nbsp;</p>
</div>

<div class='level1'>
- **Change spacing between lines** \
```css
body {
    line-height: 22.5pt;    
}
```
<p style="margin-bottom: -10px;">&nbsp;</p>
</div>

<div class='level2'>
- **Some selector examples** \
Useful explanation from <https://stackoverflow.com/questions/19931351/css-selectors-difference-between-body-h1-body-h1-and-body-h1>:
```text
* body.h1 will select the body element if it has a class of h1.
    (ex. <body class='h1'>this one</body>)
* body h1 will select all h1 elements in the body.
    (ex. <body><h1>this one</h1></body>)
    This is redundant in well-formed HTML, it will basically do the same thing as h1, 
    because the only place an h1 element can be (if your HTML is well-formed) is in the body)
* body .h1 will select all the elements that have the h1 class in the body.
    (ex. <body><div class='h1'>this one</div></body>)
```
<p style="margin-bottom: -10px;">&nbsp;</p>
</div>

<div class='level1'>
- **How to select parent but not its children** \
Useful explanation: <https://stackoverflow.com/questions/38520419/how-to-select-parent-and-not-child-in-css>.
<p style="margin-bottom: -10px;">&nbsp;</p>
</div>

<div class='level2'>
- **Select by lack of a certain property** \
Useful explanation: <https://stackoverflow.com/questions/30835168/is-there-an-opposite-css-pseudo-class-to-hover>  
Example:
```css
.child:not(:hover){
opacity: 0.3;
}
```
<p style="margin-bottom: -10px;">&nbsp;</p>
</div>

<div class='level1'>
- **Hiding objects** \
Objects like tables, paragraphs, etc, can be hidden via at least two CSS properties: "display: none;" and "visibility: hidden;" \
But, using "visibility: hidden;" does not remove the space in the page occupied by such HTML object, while "display: none;" does.
<p style="margin-bottom: -10px;">&nbsp;</p>
</div>

<div class='level2'>
- **Color linear gradient** \
Example: \
```css
td {
    background-image: linear-gradient(to right,rgba(255, 0, 0, 1) 50%,rgba(0, 0, 255, 1) 51%);
}
```
Such example splits the background color of the cells in a table with the
left half as red and the right half as blue. \
Change the percentages to determine how the color gradient is applied.
<p style="margin-bottom: -10px;">&nbsp;</p>
</div>

<div class='level2'>
- **Hide scrollbar but retain functionality** \
In the following example, the class named `hidden-scroll` is the class of a tag which
can be scrolled, but its scroll bar is not shown. \
This option can be very useful for long math equations displayed on a HTML document, due
to the limitations of the MathJax library and how it displays LaTeX equations as images.
```css
/* Hide scrollbar for Chrome, Safari and Opera */
.hidden-scroll::-webkit-scrollbar {
    display: none;
}

/* Hide scrollbar for IE, Edge and Firefox */
.hidden-scroll {
    -ms-overflow-style: none;  /* IE and Edge */
    scrollbar-width: none;     /* Firefox */
}
```
<p style="margin-bottom: -10px;">&nbsp;</p>
</div>
